Model of lens candidates from Space Warps CFHTLS

### 2016-06-24 paper2.tex
editing

. topleft: user input; top right: resulting contour map of arrival
time surface; mid left: synthetic image, renering a conical profile
source behind the modelled lens; mid right: mass profile\todo{Fix
  distance factor in $\kappa$.}  ; bottom: lensing mass, obtained from
the model against estimate of stellar mass, obtained using photometric
redshift assuming \todo{which population model?}

@@

Plausible

@@

Uncertain

@@

@@

>>>>

In this section, we discuss ten systems.

@@

@@

@@

\begin{itemize}

\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
  convincing lens candidates.

\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
  is doubtful.

\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
  candidates.

\item Figures~\ref{fig:SW36} and \ref{fig:SW57} shows {\em unclear\/}
  cases where modelling failed.

\end{itemize}

Each of Figures~\ref{fig:SW28}--\ref{fig:SW57} show six panels, as
follows.

\begin{itemize}

\item The upper left panel show a cutout of the Space~Warps image,
  marked up with a spaghetti diagram.

\item Middle left is a contour map of the arrival-time surface after
  modelling.

\item Lower left is synthetic image.
  Figures~\ref{fig:SW28}--\ref{fig:SW29} include source fitting.
  Figures~\ref{fig:SW42}--\ref{fig:SW57} uses a simple conical
  profile.

\item Upper right is a mass map.

\item Middle right shows a circularly averaged profile of
  $\kappa$.\todo{Fix distance factor in $\kappa$.}

\item Lower right shows stellar vs stellar mass.\todo{which population
  model?}

\end{itemize}

@@

SW42
